scikit-image, a Python library for 2D and 3D image processing

### 2016-08-16 skimage_tomo.tex
Fix Stéfan's name
Update my affiliation

\author[
   addressref={aff1},                   % id's of addresses, e.g. {aff1,aff2}
   corref={aff1},                       % id of corresponding address, if any
   %noteref={n1},                        % id's of article notes, if any
   email={emmanuelle.gouillart@saint-gobain.com}   % email address
]{\fnm{Emmanuelle} \snm{Gouillart}}
\author[
   addressref={aff2},
   %email={}
]{\fnm{Juan} \snm{Nunez-Iglesias}}
\author[
   addressref={aff3},
   email={stefanv@berkeley.edu}
]{\fnm{Stéfan} \snm{Van der Walt}}

@@

\address[id=aff1]{%                           % unique id
  \orgname{Surface du Verre et Interfaces, UMR 125 CNRS/Saint-Gobain}, % university, etc                     %
  \postcode{93303}                                % post or zip code
  \city{Aubervilliers},                              % city
  \cny{France}                                    % country
}
\address[id=aff2]{%
  \orgname{Life Sciences Computation Centre, University of Melbourne},
  %\street{D\"{u}sternbrooker Weg 20},
  %\postcode{24105}
  \city{Melbourne},
  \cny{Australia}
}
\address[id=aff3]{%
  \orgname{Division of Applied Mathematics, Stellenbosch University},
  %\street{D\"{u}sternbrooker Weg 20},
  %\postcode{24105}
  \city{Stellenbosch},
  \cny{South Africa}
}

>>>>

\author[
   addressref={aff1},                   % id's of addresses, e.g. {aff1,aff2}
   corref={aff1},                       % id of corresponding address, if any
   %noteref={n1},                        % id's of article notes, if any
   email={emmanuelle.gouillart@saint-gobain.com}   % email address
]{\fnm{Emmanuelle} \snm{Gouillart}}
\author[
   addressref={aff2},
   %email={}
]{\fnm{Juan} \snm{Nunez-Iglesias}}
\author[
   addressref={aff3},
   email={stefanv@berkeley.edu}
]{\fnm{Stéfan} \snm{van der Walt}}

@@

\address[id=aff1]{%                           % unique id
  \orgname{Surface du Verre et Interfaces, UMR 125 CNRS/Saint-Gobain}, % university, etc                     %
  \postcode{93303}                                % post or zip code
  \city{Aubervilliers},                              % city
  \cny{France}                                    % country
}
\address[id=aff2]{%
  \orgname{Victorian Life Sciences Computation Initiative, University of Melbourne},
  %\street{700 Swanston St},
  %\postcode{3053}
  \city{Carlton, VIC},
  \cny{Australia}
}
\address[id=aff3]{%
  \orgname{Division of Applied Mathematics, Stellenbosch University},
  %\street{D\"{u}sternbrooker Weg 20},
  %\postcode{24105}
  \city{Stellenbosch},
  \cny{South Africa}
}
